Navigating Hostility: The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space

### 2025-01-22 README.qmd
Change title
Update readme

---
format: gfm
---

@@

library(emoji)
```

# Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

@@

<!-- badges: start -->
<!-- badges: end -->

@@

Non-governmental organizations (NGOs) are a core component of global governance. Over the last two decades, however, many host governments have cracked down on NGOs using a series of laws that adversely affect the availability and use of traditional NGO funding. In response to this dramatic shift in the funding landscape, international NGOs have increasingly turned to individual donors to offset the loss funding. Prior research on NGO fundraising has examined how financial transparency and organizational accountability influence individual donor behavior. How do these elements of private donor decision-making interact with structural-level factors such as worsening host country civic environments when deciding to donate? Using a conjoint experiment with likely donors in the US, we find that transparency and accountability can protect against the dampening effect of host government crackdown and criticism of NGOs. Our results have important implications for how NGOs can adapt to worsening civic environments.

### `r emoji_glue(":zipper_mouth_face::sun_behind_large_cloud::person_walking:")`: Note on "silent skywalk" project name

>>>>

---
title: "Navigating Hostility: The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space"
format: 
  gfm: 
    wrap: preserve
    toc: true
  typst:
    toc: true
    toc-title: " "
    include-in-header: README_stuff/better-layout.typ
    author:
    - name: Suparna Chaudhry
      affiliation: Lewis and Clark College
      orcid: 0000-0003-3506-7590
      url: https://www.suparnachaudhry.com/
      email: schaudhry@lclark.edu
    - name: Marc Dotson
      affiliation: Utah State University
      orcid: 0000-0001-7846-3660
      url: https://occasionaldivergences.com/
      email: marc.dotson@usu.edu
    - name: Andrew Heiss
      affiliation: Georgia State University
      orcid: 0000-0002-3948-3914
      url: https://www.andrewheiss.com
      email: aheiss@gsu.edu
---

@@

library(emoji)

manuscript_target <- targets::tar_read(manuscript)

yaml_metadata <- rmarkdown::yaml_front_matter(here::here("manuscript", "manuscript.qmd"))
title <- yaml_metadata$title
abstract <- yaml_metadata$abstract

if (knitr::pandoc_to() == "typst") {
  # typst doesn't support emoji as of 0.11.0, so we include SVG versions from 
  # Noto Emoji (https://github.com/googlefonts/noto-emoji) instead
  emoji_out <- "![](README_stuff/noto-emoji-svgs/emoji_u1f910.svg){height=1em}![](README_stuff/noto-emoji-svgs/emoji_u1f325.svg){height=1em}![](README_stuff/noto-emoji-svgs/emoji_u1f6b6.svg){height=1em}"
} else {
  emoji_out <- emoji_glue(":zipper_mouth_face::sun_behind_large_cloud::person_walking:")
}
```

::: {.content-visible when-format="markdown"}

@@

<!-- badges: start -->
[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fhu6a5-blue)](https://doi.org/10.31235/osf.io/hu6a5) [![OSF DOI](https://img.shields.io/badge/OSF%20project-10.17605%2FOSF.IO%2FR59XZ-blue)](https://doi.org/10.17605/OSF.IO/R59XZ) [![Code DOI](https://img.shields.io/badge/Code-10.5281%2Fzenodo.14220206-blue)](https://doi.org/10.5281/zenodo.14220206)
<!-- badges: end -->

:::

@@

`r abstract`

## `r emoji_out`: Note on "silent skywalk" project name
